Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-06 Manuscript.Rmd
Added a notes section to aid the restructuring of the paper, and removed the meta-analysis from the community detection script (unneeded)

@@

Make sure to emphasize that the high overlap between sliding windows makes it more likely that differences are due to noise in the signal, and not strong variability. Like, you wouldn't expect the actual network distribution to shift that much after shifting the time series by 1 minute.g

>>>>

## Ideas to do

- The new manuscript organization could go like this: 
1) Meta-analysis and ROIs
2) Summary all
  a) Make sure to report mean density and algebraic connectivity
  b) Cross-method agreement
  c) Spatially averaged community maps reproduce group-level analysis
3) Sliding window
  a) Fiedler vector magnitude as a proxy for affiliation strength
  b) Proportion DMN for mPFC and PCC separately to denote overall stability
  b) Proportion DMN across time-series ~ fiedler vector value (consider renaming propDMN to stability)
4) Threshold the maps and rerun summary all
5) Day 1 vs day 2
6) Session
7) Potential noise
8) Structural correspondence
9) Community > correlation

@@

Make sure to emphasize that the high overlap between sliding windows makes it more likely that differences are due to noise in the signal, and not strong variability. Like, you wouldn't expect the actual network distribution to shift that much after shifting the time series by 1 minute.
